---
title: "Data cleaning and analysis"
author: "Iris Zhong"
date: "3/28/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(mosaic)
#library(sjmisc)
#library(jtools)
library(patchwork)
library(rstatix)

```

```{r read data}
library(readxl)
all_child <- read_excel("data_all_child.xlsx")


#all_child <- read_csv("C:/Users/iris_/OneDrive/Desktop/Smith/Honor #thesis/data_all_child.csv")

```

# Predictions

If child uses Rule (a): \

LLRRLRLRRL


If child uses Rule (b): \

RRLLRLRRRL

(L = select left, R = select right)


# Data Cleaning

## Remove incomplete/preview data

```{r filter incomplete preview data}
clean_child <- all_child %>%
  filter(response__is_preview == F)

clean_child %>%
  filter(response__completed == F)

clean_child <- clean_child %>%
  filter(response__completed == T)
```


## Check children only choosing left/right

```{r choose only left}
all_child %>%
  filter(item1 == "left" & item2 == "left" & item3 == "left" & item4 == "left" & item5 == "left" & item6 == "left" & item7 == "left" & item8 == "left" & item9 == "left" & item10 == "left")
```

```{r choose only right}
all_child %>%
  filter(item1 == "right" & item2 == "right" & item3 == "right" & item4 == "right" & item5 == "right" & item6 == "right" & item7 == "right" & item8 == "right" & item9 == "right" & item10 == "right")
```

35158, 36378, 36843, 33920


## Remove child who did the test twice

```{r did test twice}
clean_child <- clean_child %>%
  filter(response__id != 33970 & response__id != 38936)
```


## Check children who only chose boy/girl

```{r only choose girl}
clean_child %>%
  filter(item2 == "right" & item3 == "right" & item5 == "right" & item7 == "left" & item9 == "right")
```

```{r only choose boy}
clean_child %>%
  filter(item2 == "left" & item3 == "left" & item5 == "left" & item7 == "right" & item9 == "left")
```

```{r remove left/right boy/girl}
small_sample <- clean_child %>%
  filter(response__id != 35158 & response__id != 36378 & response__id != 36843& response__id != 33920) %>%
  filter (item2 != "right" | item3 != "right" | item5 != "right" | item7 != "left" | item9 != "right") %>%
   filter(item2 != "left" | item3 != "left" | item5 != "left" | item7 != "right" | item9 != "left")
  
```


## Remove child with significant birthdate difference

```{r remove birth diff child}
small_sample <- small_sample %>%
  filter(response__id != 33339 & response__id != 40238)
```



# Final Sample Descriptive Statistics

## Check age 

```{r clean age}
clean_child <- clean_child %>%
  mutate(age = child__age_rounded / 365)

small_sample <- small_sample %>%
  mutate(age = child__age_rounded / 365)

```


```{r check age}
favstats(clean_child$age)
favstats(small_sample$age)
```

```{r group age}
small_sample <- small_sample %>%
  mutate(age_group = case_when(age < 5 ~ 1,
                               age >=5 & age < 6 ~ 2,
                               age >=6 & age < 7 ~ 3,
                               age >= 7 ~ 4)) %>%
  mutate(age_group = as.factor(age_group))
```


## Check balance

```{r check balance}
tally(small_sample$condition_id)
tally(small_sample$age_group)
```

# Recoding

LLRRLRLRRL
RRLLRLRRRL


```{r}
small_sample_coded <- small_sample %>%
  mutate(item1=recode(item1, 
                         `left`="pi",
                         `right`="ta"),
         item2=recode(item2, 
                         `left`="pi",
                         `right`="ta"),
         item3=recode(item3, 
                         `left`="ta",
                         `right`="pi"),
         item4=recode(item4, 
                         `left`="ta",
                         `right`="pi"),
         item5=recode(item5, 
                         `left`="pi",
                         `right`="ta"),
         item6=recode(item6, 
                         `left`="ta",
                         `right`="pi"),
          item7=recode(item7, 
                         `left`="pi",
                         `right`="ta"),
         item8=recode(item8, 
                         `left`="pi",
                         `right`="ta"),
         item9=recode(item9, 
                         `left`="pi",
                         `right`="ta"),
         item10=recode(item10, 
                         `left`="ta",
                         `right`="ma")
         ) %>%
  mutate(condition_id = case_when(condition_id == "V0" ~ "2",
                                  condition_id == "V1" ~ "1")) %>%
  mutate(condition_id = as.factor(condition_id))

small_sample_coded[37, 12] = NA # remove single cell value b/c of tech issue
small_sample_coded[34, 12] = NA # remove single cell value b/c of tech issue
```




# Item 1 to 7

## Predictions

**Using Tolearnce Principle** \

Rule (a): use pi all the time in item 1-7 \
Rule (b): use ta all the time in item 1-7 \

**Using Probability Matching** \

If in Condition 1: use ta 57% of the time \
If in Condition 2: use ta 74% of the time \


**Choosing by chance** \

Use ta about 50% of the time \

## Select and Wrangle Item 1-7

```{r select and wrangle 1-7}
small_sample_AA <- small_sample_coded %>%
  select(-c(item8,item9,item10))

small_sample_AA$one_seven_ta_count <- apply(small_sample_AA, 1, function(x) length(which(x=="ta")))

#small_sample_AA <- row_count(small_sample_AA, count = "ta", append = TRUE)
small_sample_AA$NA_count <- rowSums(is.na(small_sample_AA))
#small_sample_AA <- small_sample_AA %>%
#  dplyr::rename(one_seven_ta_count = rowcount)

small_sample_AA <- small_sample_AA %>%
  mutate(ta_proportion = one_seven_ta_count/(7-NA_count)) %>%
  mutate(pi_proportion = (7-NA_count-one_seven_ta_count)/(7-NA_count))
```


```{r, include = F}
ggplot(small_sample_AA, aes(x = one_seven_ta_count, color = condition_id, fill = condition_id)) +
  geom_histogram(position = "identity", alpha = 0.5)
```

```{r, include = F}
ggplot(small_sample_AA) + geom_freqpoly(aes(x = one_seven_ta_count,
     y = ..density.., colour = condition_id)) +
  facet_wrap(~condition_id)

```

```{r,include = F}
#summary_AA <- small_sample_AA %>%
#  group_by(condition_id) %>%
#  summarize(n = n(),
#            average_proportion = mean(ta_proportion))
```

```{r,include = F}
#ggplot(small_sample_AA, aes(x=age_group, y= ta_proportion, color = age_group)) + 
#  geom_boxplot(outlier.colour="red", outlier.shape=8,
#                outlier.size=4) +
#  geom_jitter(shape=16, position=position_jitter(0.2))
```

## Number of people in each group

```{r count people by age group*condition}
small_sample_AA %>%
  group_by(condition_id, age_group) %>%
  summarize(n = n())

#library("writexl")
#write_xlsx(small_sample_AA,"item1_to_7.xlsx")
```

## Descrptive Stats

```{r item1-7 descriptive}
favstats(small_sample_AA$ta_proportion)
favstats(ta_proportion~condition_id, data = small_sample_AA)
favstats(data = small_sample_AA, ta_proportion~age_group)
tally(small_sample_AA$age_group)

```

```{r}
ggplot(small_sample_AA, aes(x = ta_proportion)) +
  geom_bar()
```

```{r item 1-7 demo}
young_AA <- small_sample_AA %>%
  filter(age<6)

old_AA <- small_sample_AA %>%
  filter(age>=6)

p1 <- ggplot(small_sample_AA, aes(x = ta_proportion)) +
  geom_bar()+
  labs(title = "Overall ta_proportion", y = "Count")

eq_a = function(x){0.0001^x}
eq_b = function(x){exp(x^6)}

exp_a <- ggplot(data.frame(x=c(0,1)), aes(x=x)) + 
  stat_function(fun=eq_a) +
  labs(x = "ta_proportion", y = "Predicted count distribution by Rule (a)") +
theme(axis.text.y = element_blank() )

exp_b <- ggplot(data.frame(x=c(0,1)), aes(x=x)) + 
  stat_function(fun=eq_b) +
  labs(x = "ta_proportion", y = "Predicted count distribution by Rule (b)") +
  theme(axis.text.y = element_blank() )

p2 <- ggplot(young_AA, aes(x = ta_proportion, fill = condition_id)) +
  geom_bar(width = 0.1) +
  facet_wrap(~condition_id) +
  labs(title = "Children younger than 6", y = "Count") +
  scale_fill_manual(values=c('#FFB646','#00AA9F'))+
  theme(legend.position = "none") 

p3 <- ggplot(old_AA, aes(x = ta_proportion, fill = condition_id)) +
  geom_bar(width = 0.1) +
  facet_wrap(~condition_id) +
  labs(title = "Children older than 6", y = "Count") +
  scale_fill_manual(values=c('#FFB646','#00AA9F'))+
  theme(legend.position = "none") +
  ylim(0,8)

p1
  
exp_a+exp_b
p2+p3
```





```{r include = F}
x <-c(0, 0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)
y1 <- exp(x^6)
y2 <- exp(-x^6)

exp_df <- data.frame(x,y1,y2)

p1_exp <- ggplot(exp_df, aes(x = x, y = y2)) +
  geom_point() +
  labs(y = "Count", x = "ta_proportion") + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks=seq(0,1,1/7), limits = c(0,1))+
  labs(title = "Expected ta_proportion for Rule (a)")

p1_exp2 <- ggplot(exp_df, aes(x = x, y = y1)) +
  geom_point() +
  labs(y = "Count", x = "ta_proportion") + 
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  scale_x_continuous(breaks=seq(0,1,1/7), limits = c(0,1))+
  labs(title = "Expected ta_proportion for Rule (b)")

```

```{r bargraph, young/old, condition1/2}

small_sample_AA <- small_sample_AA %>%
  mutate(young_old = ifelse(age_group == 1 | age_group == 2, 0, 1)) %>%
  mutate(young_old = as.factor(young_old))

means_AA <- small_sample_AA %>% 
  group_by(condition_id, young_old) %>% 
   summarise(mean = mean(ta_proportion),
             se = sd(ta_proportion) / sqrt(length(ta_proportion)))

# making the plot
ggplot(means_AA, aes(x=condition_id, y=mean, fill=young_old)) + 
  geom_bar(stat="identity", 
           position=position_dodge(), width=0.5) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2,
                 position=position_dodge(.5)) +
  ylim(0,1) +
  geom_hline(yintercept=0.5, linetype='dashed', col = '#005FA7') +
  labs(x = "Condition", y = "Average ta_proportion", fill = "Children age")+
  scale_fill_manual(labels = c("Younger than 6", "Older than 6"), values=c('#FFB646','#00AA9F'))

```

```{r young old test}
wilcox_test(small_sample_AA,ta_proportion~young_old)
```

```{r young old anova test}
anova2 <- aov(ta_proportion ~ condition_id * young_old, data = small_sample_AA)
summary(anova2)
```



## Boxplot

```{r item 1-7 ta boxplot}
ggplot(small_sample_AA, aes(age_group, ta_proportion, fill = age_group))+
  stat_boxplot(aes(age_group, ta_proportion), 
    geom='errorbar', linetype=1, width=0.5)+  #whiskers
  geom_boxplot(aes(age_group, ta_proportion),outlier.shape=8) + 
  scale_fill_manual(values=c("#FFD08C", "#AD99D7", "#7AAE82","#FFAEAE"))+
  stat_summary(fun.y=mean, geom="point", size=2) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.3, color = "#DB4642") +
  facet_wrap(~condition_id) +
  geom_hline(yintercept=0.5, linetype='dashed', col = '#005FA7') +
  geom_jitter(color="black", size=1, alpha=0.3, height = 0) +
  labs(title = "percentage of answering 'ta' in first seven items", subtitle = "separated by condition", x = "Age group")  +
  theme(legend.position = "none")
```



```{r item 1-7 pi boxplot, include = F}
ggplot(small_sample_AA, aes(age_group, pi_proportion))+
  stat_boxplot(aes(age_group, pi_proportion), 
    geom='errorbar', linetype=1, width=0.5)+  #whiskers
  geom_boxplot(aes(age_group, pi_proportion),outlier.shape=8) +    
  stat_summary(fun.y=mean, geom="point", size=2) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.3, color = "red") +
  facet_wrap(~condition_id) +
  geom_hline(yintercept=0.5, linetype='dotted', col = 'blue') +
  geom_jitter(color="black", size=1, alpha=0.3, height = 0) +
  labs(title = "percentage of answering 'pi' in first seven items", subtitle = "separated by condition")
```




## Interaction Plot


```{r interaction plot}
ggplot(small_sample_AA, aes(x=age, y=ta_proportion, shape=condition_id, color=condition_id)) +
  geom_point()+
  geom_smooth(method=lm,aes(fill=condition_id), level = 0.95) +
  labs(x = "Age") +
  scale_fill_manual(values=c("#FFB646", "#00AA9F")) +
  scale_color_manual(values=c("#FFB646", "#00AA9F")) +
  guides(col=guide_legend("Condition"),
         shape = guide_legend("Condition"),
         fill = guide_legend("Condition"))
  
```

## Regression

A regression to see if there's an interaction between age (continuous) and condition_id: 

```{r regession age*condition}
lm1<-lm(ta_proportion~age*relevel(condition_id, ref = "2"),data=small_sample_AA)
summary(lm1)
```


There is an interaction between age and condition_id! But R^2 is small. 



Check the regression assumptions

```{r residual plot}
plot(predict(lm1),resid(lm1),col="midnightblue",pch=18,main="Residual plot")
abline(0,0,col="red")
```

```{r normal Q-Q plot}
qqnorm(resid(lm1),pch=19)
qqline(resid(lm1),col="red")
```

```{r regression shapiro}
shapiro.test(resid(lm1))
```

```{r, include = F}
lm2<-lm(ta_proportion~age_group*condition_id,data=small_sample_AA)
summary(lm2)
```


## ANOVA

Condition by age group


```{r ANOVA condition*age group}
anova1 <- aov(ta_proportion ~ condition_id * age_group, data = small_sample_AA)
summary(anova1)
```



## Non-parametric tests

### ta_proportion ~ Condition

independent 2-group Mann-Whitney U Test: 
Is ta_proportion different in Condition 1 vs. Condition 2 for items 1-7

```{r ta_proportion ~ condition}
wilcox_test(small_sample_AA,ta_proportion~condition_id)
```

### ta_proportion ~ age group

Kruskal Wallis Test One Way Anova by Ranks:

Is ta_proportion different among age groups

```{r ta_proportion ~ age groups}
kruskal.test(small_sample_AA$ta_proportion~small_sample_AA$age_group)
```

No effect of age group.


## Hypothesis testing

### Do children use the Tolerance Principle?

#### Prediction

ta_proportion is not significantly different from 0 or 1.

test normality:
```{r shapiro ta_proportion}
shapiro.test(small_sample_AA$ta_proportion)
```

Not normal!! Cannot use t-test; non-parametric tests instead.

#### Compare ta_proportion with 0 and 1


```{r item 1-7 TP}
wilcox.test(small_sample_AA$ta_proportion, mu = 1, alternative = "two.sided")
wilcox.test(small_sample_AA$ta_proportion, mu = 0, alternative = "two.sided")
```

ta_proportion is not significantly different from 1 nor 0. (Not what I wish to see!)

#### Compare ta_proportion with 0.5

Are they choosing randomly (i.e. is it different from 0.5?)

```{r item 1-7 0.5}
wilcox.test(small_sample_AA$ta_proportion, mu = 0.5, alternative = "two.sided")
```

ta_proportion is not significantly different from 0.5. 


#### Do children use separate rules?

Maybe children have separate rules learned?

```{r filter by ta_proportion}
# Filter out children who choose pi_proportion >= 0.5

large_pi_AA <- small_sample_AA %>%
  filter(pi_proportion >= 0.5)

# Filter out children who choose pi_proportion <= 0.5

small_pi_AA <- small_sample_AA %>%
  filter(pi_proportion <= 0.5)

nrow(large_pi_AA) # small ta
nrow(small_pi_AA) # large ta

```



Do the non-parametric test (and t-test) again: 

```{r item 1-7 TP test filtered by ta_proportion}
wilcox.test(large_pi_AA$ta_proportion, mu = 0, alternative = "two.sided")
wilcox.test(small_pi_AA$ta_proportion, mu = 1, alternative = "two.sided")
t.test(small_pi_AA$ta_proportion, mu = 1, alternative = "two.sided")
t.test(small_pi_AA$ta_proportion, mu = 1, alternative = "two.sided")
```


```{r include = F}
consistent_AA <- small_sample_AA %>%
  filter(ta_proportion > 0.7 | ta_proportion < 0.3)
```


### Do children use probability matching? 

#### Are they significantly different from token frequency?
1: 0.57 ta
2: 0.74 ta

```{r item 1-7 PM}
AA_condition1 <- small_sample_AA %>% filter(condition_id == "1") 
AA_condition2 <- small_sample_AA %>% filter(condition_id == "2") 
wilcox.test(AA_condition1$ta_proportion, mu = 0.57, alternative = "two.sided")
wilcox.test(AA_condition2$ta_proportion, mu = 0.74, alternative = "two.sided")
t.test(AA_condition1$ta_proportion, mu = 0.57, alternative = "two.sided")
t.test(AA_condition2$ta_proportion, mu = 0.74, alternative = "two.sided")
```
Condition 2 significantly different from probability; but Condition 1 is not.


#### Are they significantly different from 0.5?

```{r item 1-7 condition chance}
wilcox.test(AA_condition1$ta_proportion, mu = 0.5, alternative = "two.sided")
wilcox.test(AA_condition2$ta_proportion, mu = 0.5, alternative = "two.sided")
```

No, ta_proportion is not significantly different from chance. 

## Do younger children differ from older children?

Maybe, older children use more probability matching. 

```{r young old item1-7 PM}


young_condition1 <- young_AA %>% filter(condition_id == "1") 
young_condition2 <- young_AA %>% filter(condition_id == "2") 
old_condition1 <- old_AA %>% filter(condition_id == "1") 
old_condition2 <- old_AA %>% filter(condition_id == "2") 
wilcox.test(young_condition1$ta_proportion, mu = 0.57, alternative = "two.sided")
wilcox.test(young_condition2$ta_proportion, mu = 0.74, alternative = "two.sided")
wilcox.test(old_condition1$ta_proportion, mu = 0.57, alternative = "two.sided")
wilcox.test(old_condition2$ta_proportion, mu = 0.74, alternative = "two.sided")
```

No. They behaved about the same. 

# Item 8 to 10

## Predictions

**Using the Tolearnce Principle** \

No matter using Rule (a) or Rule (b), should choose ta all the time \

**Using Probability Matching** \

If in Condition 1: use ta 57% of the time \
If in Condition 2: use ta 74% of the time \
But they should answer Item 10 the ta marker all the time, because it is a check question.\

**Choosing by chance** \

Choosing ta around 50% of the time. 


## Select and wrangle Item 8-10

```{r select and wrangle 8-10}
small_sample_AB <- small_sample_coded %>%
  dplyr::select(-c(item1:item7))

small_sample_AB$eight_ten_ta_count <- apply(small_sample_AB, 1, function(x) length(which(x=="ta")))

#small_sample_AB <- row_count(small_sample_AB, count = "ta", append = TRUE)
small_sample_AB$NA_count <- rowSums(is.na(small_sample_AB))

small_sample_AB <- small_sample_AB %>%
#  dplyr::rename(eight_ten_ta_count = rowcount) %>%
  mutate(ta_proportion = (eight_ten_ta_count / 3))
```


## Descrptive stats

```{r item 8-10 descrptive stats}
tally(small_sample_coded$item8)
tally(small_sample_coded$item9)
tally(small_sample_coded$item10)

favstats(ta_proportion ~ condition_id, data = small_sample_AB)
favstats(ta_proportion ~ age_group, data = small_sample_AB)
```

## Boxplot


```{r item 8-10 ta_proportion boxplot, include = F}
ggplot(small_sample_AB, aes(age_group, ta_proportion))+
  stat_boxplot(aes(age_group, ta_proportion), 
    geom='errorbar', linetype=1, width=0.5)+  #whiskers
  geom_boxplot(aes(age_group, ta_proportion),outlier.shape=8) +    
  stat_summary(fun.y=mean, geom="point", size=2) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.3, color = "red") +
  facet_wrap(~condition_id) +
  geom_hline(yintercept=1, linetype='dotted', col = 'blue') +
  geom_jitter(color="black", size=1, alpha=0.3, height = 0) +
  labs(title = "percentage of answering 'ta' in last three items", subtitle = "separated by condition")
```

```{r}
ggplot(small_sample_AB, aes(age_group, ta_proportion, fill = age_group))+
  stat_boxplot(aes(age_group, ta_proportion), 
    geom='errorbar', linetype=1, width=0.5)+  #whiskers
  geom_boxplot(aes(age_group, ta_proportion),outlier.shape=8) + 
  scale_fill_manual(values=c("#FFD08C", "#AD99D7", "#7AAE82","#FFAEAE"))+
  stat_summary(fun.y=mean, geom="point", size=2) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.3, color = "#DB4642") +
  facet_wrap(~condition_id) +
  geom_hline(yintercept=1, linetype='dashed', col = '#005FA7') +
  geom_jitter(color="black", size=1, alpha=0.3, height = 0) +
  labs(title = "percentage of answering 'ta' in last three items", subtitle = "separated by condition", x = "Age group")  +
  theme(legend.position = "none")
```


## Regression

Does age/condition ID have effect on ta_proportion in Item 8-10?


```{r item 8-10 regression ta_proportion~age*condition}
lm3 <- lm(ta_proportion~age*relevel(condition_id, ref = "2"),data=small_sample_AB)
summary(lm3) 
```

## Hypothesis testing

### Do children use the Tolerance Principle?

```{r item 8-10 TP}
wilcox.test(small_sample_AB$ta_proportion, mu = 1, alternative = "two.sided")
```

### Do children recognize the difference between AA and AB?

```{r test ta_proportion difference between AA and AB}
sample_join <-small_sample_AB %>%
  full_join(small_sample_AA, by = "response__id") %>%
  dplyr::select(response__id, age_group = age_group.x, AB_ta_proportion = ta_proportion.x, AA_ta_proportion = ta_proportion.y)

wilcox.test(sample_join$AB_ta_proportion, sample_join$AA_ta_proportion, paired = TRUE, alternative = "two.sided")
```

Not significantly different.


### Do children use probability matching?

```{r item 8-10 PM}
AB_condition1 <- small_sample_AB %>% filter(condition_id == "1") 
AB_condition2 <- small_sample_AB %>% filter(condition_id == "2") 
wilcox.test(AB_condition1$ta_proportion, mu = 0.57, alternative = "two.sided")
wilcox.test(AB_condition2$ta_proportion, mu = 0.74, alternative = "two.sided")
wilcox.test(AB_condition1$ta_proportion, mu = 0.5, alternative = "two.sided")
wilcox.test(AB_condition2$ta_proportion, mu = 0.5, alternative = "two.sided")
```

Condition 2 significantly different from probability; but Condition 1 is not. Both are not significantly different from chance. 



```{r item by item, include = F}
small_sample_all <- small_sample_coded %>%
  mutate(item1_r = case_when(item1 == "ta" ~ 1,
                             item1 == "pi" ~ 0),
         item2_r = case_when(item2 == "ta" ~ 1,
                             item2 == "pi" ~ 0),
         item3_r = case_when(item3 == "ta" ~ 1,
                             item3 == "pi" ~ 0),
         item4_r = case_when(item4 == "ta" ~ 1,
                             item4 == "pi" ~ 0),
         item5_r = case_when(item5 == "ta" ~ 1,
                             item5 == "pi" ~ 0),
         item6_r = case_when(item6 == "ta" ~ 1,
                             item6 == "pi" ~ 0),
         item7_r = case_when(item7 == "ta" ~ 1,
                             item7 == "pi" ~ 0),
         item8_r = case_when(item8 == "ta" ~ 1,
                             item8 == "pi" ~ 0),
         item9_r = case_when(item9 == "ta" ~ 1,
                             item9 == "pi" ~ 0),
         item10_r = case_when(item10 == "ta" ~ 1,
                             item10 == "ma" ~ 0),)

all_items_condition <- small_sample_all %>%
  group_by(condition_id) %>%
  summarize(item1_mean = mean(item1_r),
            item2_mean = mean(item2_r),
            item3_mean = mean(na.omit(item3_r)),
            item4_mean = mean(item4_r),
            item5_mean = mean(item5_r),
            item6_mean = mean(item6_r),
            item7_mean = mean(na.omit(item7_r)),
            item8_mean = mean(item8_r),
            item9_mean = mean(item9_r),
            item10_mean = mean(item10_r)) %>%
  pivot_longer(cols = item1_mean:item10_mean,names_to = "item_num", values_to = "item_mean")

ggplot(all_items_condition, aes(x = item_num, y = item_mean, color = condition_id, fill = condition_id)) +
  geom_col(position=position_dodge(), width = 0.5)

all_items_age <- small_sample_all %>%
  group_by(age_group) %>%
  summarize(item1_mean = mean(item1_r),
            item2_mean = mean(item2_r),
            item3_mean = mean(na.omit(item3_r)),
            item4_mean = mean(item4_r),
            item5_mean = mean(item5_r),
            item6_mean = mean(item6_r),
            item7_mean = mean(na.omit(item7_r)),
            item8_mean = mean(item8_r),
            item9_mean = mean(item9_r),
            item10_mean = mean(item10_r))
```



# Only children answering Item 10 correctly

How about filtering out children who answered Item 10 incorrectly? \
Look at their Item1-7 again. 

## Filtering 

```{r filter item10 correct child}
item10_correct_AA <- small_sample_coded %>%
  filter(item10 == "ta") %>%
  select(-c(item8,item9,item10))

item10_correct_AA$one_seven_ta_count <- apply(item10_correct_AA, 1, function(x) length(which(x=="ta")))

#item10_correct_AA <- row_count(item10_correct_AA, count = "ta", append = TRUE)
item10_correct_AA$NA_count <- rowSums(is.na(item10_correct_AA))

#item10_correct_AA <- item10_correct_AA %>%
#  dplyr::rename(one_seven_ta_count = rowcount)

item10_correct_AA <- item10_correct_AA %>%
  mutate(ta_proportion = one_seven_ta_count/(7-NA_count)) %>%
  mutate(pi_proportion = (7-NA_count-one_seven_ta_count)/(7-NA_count))
  
```


```{r filter item10 wrong child}
item10_wrong_AA <- small_sample_coded %>%
  filter(item10 != "ta") %>%
  select(-c(item8,item9,item10))

item10_wrong_AA$one_seven_ta_count <- apply(item10_wrong_AA, 1, function(x) length(which(x=="ta")))

#item10_wrong_AA <- row_count(item10_wrong_AA, count = "ta", append = TRUE)
item10_wrong_AA$NA_count <- rowSums(is.na(item10_wrong_AA))

#item10_wrong_AA <- item10_wrong_AA %>%
#  dplyr::rename(one_seven_ta_count = rowcount)

item10_wrong_AA <- item10_wrong_AA %>%
  mutate(ta_proportion = one_seven_ta_count/(7-NA_count)) %>%
  mutate(pi_proportion = (7-NA_count-one_seven_ta_count)/(7-NA_count))
  
```

```{r, include = F}
ggplot(item10_wrong_AA, aes(x = ta_proportion)) +
  geom_bar() +
  facet_wrap(~condition_id)
```

```{r include = F}
ggplot(item10_correct_AA, aes(x = ta_proportion)) +
  geom_bar() +
  facet_wrap(~condition_id)
```

## Hypothesis testing

### Are they using the Tolerance Principle?


```{r item10 child TP}
wilcox.test(item10_correct_AA$ta_proportion, mu = 1, alternative = "two.sided")
wilcox.test(item10_correct_AA$ta_proportion, mu = 0, alternative = "two.sided")
wilcox.test(item10_correct_AA$ta_proportion, mu = 0.5, alternative = "two.sided")
t.test(item10_correct_AA$ta_proportion, mu = 1, alternative = "two.sided")
t.test(item10_correct_AA$ta_proportion, mu = 0, alternative = "two.sided")
```

No, and still not significantly different from chance.




### Are they using probability matching?


```{r item10 correct child PM}
AA_condition1_correct <- item10_correct_AA %>% filter(condition_id == "1") 
AA_condition2_correct <- item10_correct_AA %>% filter(condition_id == "2") 
wilcox.test(AA_condition1_correct$ta_proportion, mu = 0.57, alternative = "two.sided")
wilcox.test(AA_condition1_correct$ta_proportion, mu = 0.5, alternative = "two.sided")
wilcox.test(AA_condition2_correct$ta_proportion, mu = 0.74, alternative = "two.sided")
t.test(AA_condition1_correct$ta_proportion, mu = 0.57, alternative = "two.sided")
t.test(AA_condition2_correct$ta_proportion, mu = 0.74, alternative = "two.sided")
```

### Is condition 1 different from condition 2, for children who answered item 10 correctly?

```{r}
wilcox.test(item10_correct_AA$ta_proportion~item10_correct_AA$condition_id)
t.test(item10_correct_AA$ta_proportion~item10_correct_AA$condition_id)
```

No they are not significantly different from each other. 

### Is there difference between young & old children for item 1-7 ta_proportion (for those item 10 is correct)?

#### Filter

```{r filter young old children item10 correct}
item10_correct_AA_young <- item10_correct_AA %>%
  filter(age<6)

item10_correct_AA_old <- item10_correct_AA %>%
  filter(age>=6)
```

#### Test probability matching

```{r item10 correct PM}
young_condition1_correct <- item10_correct_AA_young %>% filter(condition_id == "1") 
young_condition2_correct <- item10_correct_AA_young %>% filter(condition_id == "2") 
old_condition1_correct <- item10_correct_AA_old %>% filter(condition_id == "1") 
old_condition2_correct <- item10_correct_AA_old %>% filter(condition_id == "2") 
wilcox.test(young_condition1_correct$ta_proportion, mu = 0.57, alternative = "two.sided")
wilcox.test(young_condition2_correct$ta_proportion, mu = 0.74, alternative = "two.sided")
wilcox.test(old_condition1_correct$ta_proportion, mu = 0.57, alternative = "two.sided")
wilcox.test(old_condition2_correct$ta_proportion, mu = 0.74, alternative = "two.sided")
wilcox.test(old_condition1_correct$ta_proportion, mu = 0.5, alternative = "two.sided")
```


Similar results. They still answered by chance. 









How many children choose categorically?

```{r}
small_sample_AA %>%
  filter(ta_proportion == 1 | ta_proportion == 0) %>%
  summarize(n = n())
```

